Verifying Spatial Properties of Stencil Computations

### 2016-11-16 paper.tex
Typographic mistake

Various deductive verification tools can express array indexing
in their specifications, \eg{}, ACSL of \citet{baudin2008acsl}
for C (see \eg{}~\citet[Example 3.4.1]{burghardt2010acsl}). Thus, a specification
can be given for a stencil computation, 
however, such a specification would exactly replicate the fine-grained
indexing seen in the code and would simply be prone to low-level input
errors. Our approach is much more abstract,
capturing the shape of a specification in concise format different to
the code.

\citet{kamil2016verified} propose \emph{verified lifting} to extract a
functionally-complete mathematical representation of low-level, and
potentially optimised, stencils in Fortran code. This extracted
predicate representation of a stencil is used to generate code
for the \textsf{Halide} high-performance
compiler~\citep{ragan2013halide}. Thus their approach must capture the
full meaning of a stencil computation which requires significant
program analysis. For example, they report that some degenerate
stencil kernels take up to 17 hours to analyse and others require
programmer intervention for correct invariants to be inferred.

@@

\section{Conclusion}\label{sec:conclusion}

We have presented a high-level language for the specification of
stencils in numerical code. As opposed to existing approaches our
language takes inspiration from the numerical literature and provides
a concise, abstract description of the stencil.

@@

Our definition of a stencil computation meant that we generated no
specification for a large number of iterated array accesses in the
corpus, such as stencils that incorporates reductions. For
future work, we will be looking into expanding the flexibility of 
our inference approach to more of these examples.

>>>>

Various deductive verification tools can express array indexing
in their specifications, \eg{}, ACSL of \citet{baudin2008acsl}
for C (see \eg{}~\citet[Example 3.4.1]{burghardt2010acsl}). Thus, a specification
can be given for a stencil computation, 
however, such a specification would exactly replicate the fine-grained
indexing seen in the code and would simply be prone to low-level input
errors. Our approach is much more abstract-- it does
not aim to reify indexing in the specification, but is novel
in that it instead
provides abstract spatial descriptions which capture a large number
of common patterns.

\citet{kamil2016verified} propose \emph{verified lifting} to extract a
functionally-complete mathematical representation of low-level, and
potentially optimised, stencils in Fortran code. This extracted
predicate representation of a stencil is used to generate code
for the \textsc{Halide} high-performance
compiler~\citep{ragan2013halide}. Thus their approach must capture the
full meaning of a stencil computation which requires significant
program analysis. For example, they report that some degenerate
stencil kernels take up to 17 hours to analyse and others require
programmer intervention for correct invariants to be inferred.

@@

\paragraph{Concluding remarks}

There is an increasing awareness of the need for verification
techniques in
science~\cite{post2005computational,oberkampf2010verification,orchard2014computational}.
Our specification language is an approach in this direction, providing
a system of lightweight, high-level specification for numerical code.
As opposed to existing approaches our language takes inspiration from
the numerical literature and provides a concise, abstract description
of the stencil.

@@

Our definition of a stencil computation meant that we generated no
specification for a large number of iterated array accesses in the
corpus, such as stencils that incorporates reductions. For
future work, we will be looking into expanding the flexibility of 
our analysis to include these examples.
